\documentclass[12pt]{article}
% \usepackage[whole]{bxcjkjatype} % for Japanese
\usepackage[margin=0.5in,noheadfoot,a4paper]{geometry}
\usepackage{natbib}
\usepackage{pmlatex}

\title{A possible target for MISIP-2015}%
\author{PML}%
\date{\today}%

\begin{document}
\maketitle
\BibliographySisyphus{20150413140738-506731} % take this line out on new report
% FILEPATH START
Last modified: \url{/Users/hk-local/Dropbox/Documents/proposal-EC-MISIP-2015/report.tex} on 2015-04-13 09:59
% FILEPATH END
\begin{abstract}
  A research proposal for MISIP-2015 is described in this document.
\end{abstract}
\tableofcontents


\section{INTRODUCTION}
Ordinary chondrites were surveyed in detail, for the Chelyabinsk
meteorite LL5 on MISIP-2013, and for Begga LL3 and Olivenza LL5 on
MISIP-2014.

To expand our comprehensive investigations for meteorites, detailed
analyses to enstatite chondrites during MISIP-2015 is proposed.


The enstatite stone-list in PML is shown in Table
\ref{tables/stone_list0}.  

Preliminary analyses made on enstatite chondrites
are summarized in Table \ref{tables/status0} and Figure
\ref{figures/figure0} \citeyearpar{20140729091146-980887}.

\input{tables/stone_list0}
\input{tables/status0}
\input{figures/figure0}

BSE image of thin section Sahara 97103 is shown in Figure
\ref{Sahara-97103/figure0}.

\input{Sahara-97103/figure0}



\section{REVIEW}
The enstatite chondrites (EC) are the most reduced type among
chondrites, and characterized by low $\rm (Mg/Si)_{bulk}$.　They
consist of two groups, EL (low Fe) and EH (high Fe).

\subsection{Elemental abundances}
\cite{Kallemeyn:1986} reported major-minor-trace element abundances of
EH3--5 and EL6 chondrites. EL and EH have clear compositional
hiatus. Siderophile and


\subsection{Oxygen isotope}
\cite{Clayton:1984} investigated oxygen isotopic compositions of EH
and EL chondrites. Mean \deltaion[18]{O} and \deltaion[17]{O} are
$5.31\pm0.45$ and $2.74\pm0.30$ for EH, and $5.57\pm0.13$ and
$2.96\pm0.06$ for EL. These abundances are indistinguishable from
terrestrial ones.

\subsection{Formation age}
Rb-Sr ages for enstatite chondrites are shown in Table
\ref{tables/table0}. \cite{Gopalan:1970} showed that whole-rock data
on the other 7 enstatite chondrites (EH and EL) plot on 4.45-Ga line.

\input{tables/table0}

\clearpage
\bibliographystyle{gca_like} % \bibliographystyle{apalike-url}
\bibliography{ref_geochem,ref_pml,ref_dream}
\listoffigures
\listoftables

\end{document}

%% platex
% \documentclass[12pt]{jarticle}
% \usepackage[expert,deluxe]{otf}
% \usepackage[dvipdfmx]{hyperref}
% \usepackage[dvipdfmx]{graphicx,color}

%% paper size
% \usepackage[paperwidth=16cm,paperheight=15cm,margin=0.2cm]{geometry}  % X220
% \usepackage[paperwidth=8.5cm,paperheight=11cm,margin=0.0cm]{geometry} % Kindle
